IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/real.tex
Title section
improve figures for one-column layout
nodejs

In the introduction, we stated that the original motivation behind
this work was to formally specify a
coarse-grained information flow control language for JavaScript.
%
Indeed, our formalism serves as the theoretical foundation for two
IFC systems for JavaScript, built on top of Node.js as well as
the web browser engine Gecko.

In this section, we describe these two implementations.  Furthermore,
we consider how our formalism could be applied to the C programming
language and connect it to a previous IFC system for Haskell.
%
The goal of this section is to show the flexibility of the embedding in settings with
vastly different properties and discuss the
semantic gap that must be overcome to apply our formalism
to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

@@

JavaScript, as specified by
ECMAScript~\cite{ecma}, does not have any built-in
functionality for I/O.
%(we denote this language as |targetLangJS|).
%
For this language, which we denote by |targetLangJS|, the IFC system
|specLangJS roundrobinf| can be implemented by exposing IFC primitives
to JavaScript as part of the runtime, and running multiple instances
of the JavaScript virtual machine in separate OS-level threads.
%
Unfortunately, this becomes very costly when an application relies on
many tasks.
%
For instance, consider a server-side web application that
creates a new task for each HTTP request.  The overhead would
quickly become impractical.

However, this issue of performance and JavaScript isolation is not
unique to our work and has been solved by browser engines,
which also
rely on the isolation of content from
different origins (e.g., two iframes of different origins) to
implement the same-origin policy.
%
Since creating an OS thread for each iframe is expensive, both
Google's V8 and Mozilla's SpiderMonkey provide a means for running
JavaScript code in isolation in a single OS thread,
on disjoint sub-heaps.
%
In V8, this unit of isolation is called a \emph{context}; in
SpiderMonkey, it is called a \emph{compartment}.
%
Each context/compartment is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
Naturally, our notion of a task for JavaScript directly corresponds to
a context/compartment.

When JavaScript is embedded in web browser engines, such as Google's
Blink or Mozilla's Gecko, or in server-side platforms such as Node.js,
additional APIs such as the Document Object Model (DOM) or the file
system get exposed as part of the runtime system.
These features are exposed by extending the global object, just like
for the standard library.  For this reason, it is easy to modify
these systems to remove arbitrary external effects when implementing
an IFC system so important effects can be reintroduced in a safe manner.

\subsubsection{Server-side IFC: Node.js}

We have implemented |specLangJS seqf| for Node.js in the form of a module
(library), which does not modify the Node.js or V8 code-base in any
way.
%
Our implementation\footnote{The source code of our implementation can be found at
  \codelink{}.} provides a library for creating new tasks, i.e.,
contexts whose global object only contains the standard JavaScript
library as well as our IFC primitives (such as |send| and |sandbox|).
%
In turn, these tasks can create new tasks with |sandbox|.
%
In our formal treatement, |sandbox| is defined with |ap klone tS = tS0|,
where |tS0| is the global object corresponding to the standard
JavaScript library and our IFC primitives.

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
All IFC primitives are mediated by the trusted library code (executing
as the main Node.js context), which tracks the current label, messages,
etc.\ of each task.  An example for |send|/|recv| is shown in
Figure~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
Our system conservatively restricts
the kinds of messages that can be exchanged by tasks by
only allowing string values to be exchanged via |send| (and |sandbox|).
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
For convenience, we have implemented a library that provides
more flexible primitives, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

While the described system implements |specLangJS seqf|, server-side
applications may require access to the file system, HTTP server, HTTP
client, or other APIs that have external effects.
%
Exposing the Node.js APIs directly to sandboxed tasks is unsafe, and
thus we
%
instead implement libraries such as a labeled file system as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
our IFC monitor.\footnote{
  Importantly, we provide mostly-identical interfaces to
  the standard Node.js libraries, hiding the underlying
  message-passing implementations.
}
%
This is safer than the approach of simply wrapping objects, which can
potentially allow objects to be accessed outside the context.
%
This task is trusted to ensures that labels are
propagated to files and the labels of the task and the file in question permit
this flow.
%
Unfortunately, while imposing such a proof burden on the
framework developer is undesirable, this also has to be expected:
different language environments expose different libraries for
handling external I/O, and the correct treatment of external effects
is application specific.
%
For instance, in the case of Node.js, how labels interact with the
file system may even vary according to the application (e.g.,
in the IFC system Hails~\cite{hails}, labels are not persisted).
%
%While we can extend our formalism to model a particular interface to
%the file system, HTTP client, etc. the utility of this formalization is
%unclear and left to future work.
%
We do not extend our formalism to account for the  particular
interface to the file system, HTTP client, etc., as this is
specific to the Node.js implementation and does not generalize
to other systems.

\subsubsection{Client-side IFC: Gecko}

We now describe some of the implementation aspects of
COWL, a JavaScript implementation of coarse-grained
IFC for Mozilla's Gecko.  This work provides the formal basis for
the implementation, and COWL is described in much more detail in~\cite{swapi}.
%
Since the architecture of COWL is similar to that of Node.js, we focus
on the main differences.

>>>>

In this section, we describe two JavaScript IFC implementations
building on the theoretical foundations of this work.
%
Furthermore, we consider how our formalism could be applied to the C
programming language and connect it to a previous IFC system for
Haskell.
%
%% The goal of this section is to show the flexibility of the embedding in settings with
%% vastly different properties and discuss the
%% semantic gap that must be overcome to apply our formalism
%% to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

@@

JavaScript, as specified by
ECMAScript~\cite{ecma}, does not have any built-in
functionality for I/O.
%(we denote this language as |targetLangJS|).
%
For this language, which we denote by |targetLangJS|, the IFC system
|specLangJS roundrobinf| can be implemented by exposing IFC primitives
to JavaScript as part of the runtime, and running multiple instances
of the JavaScript virtual machine in separate OS-level threads.
%
Unfortunately, this becomes very costly when a system, such as a
server-side web application, relies on many tasks.
%
%% For instance, consider a server-side web application that
%% creates a new task for each HTTP request.  The overhead would
%% quickly become impractical.

Luckly, this issue is not unique to our work---browser layout engines
also rely isolating code of different origins (e.g., according to the
same-origin policy).
%
Since creating an OS thread for each iframe is expensive, both
the V8 and SpiderMonkey JavaScript engines provide a means for running
JavaScript code in isolation in a single OS thread,
on disjoint sub-heaps.
%
In V8, this unit of isolation is called a \emph{context}; in
SpiderMonkey, it is called a \emph{compartment}.
%
(We will use these terms interchangably.)
%
Each context is associated with a global object, which, by
default, implements the JavaScript standard library (e.g.,
\verb|Object|, \verb|Array|, etc.).
%
Naturally, we adopt contexts to implement our notion of tasks.

When JavaScript is embedded in browser layout engines, 
or in server-side platforms such as Node.js,
additional APIs such as the Document Object Model (DOM) or the file
system get exposed as part of the runtime system.
These features are exposed by extending the global object, just like
the standard library.  For this reason, it is easy to modify
these systems to remove arbitrary external effects when implementing
an IFC system so important effects can be reintroduced in a safe manner.

\begin{figure}[t]
\centerline{\includegraphics[width=0.7\columnwidth]{figs/node}}
\caption{\label{fig:node}
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
\subsubsection{Server-side Node.js IFC:}\ 
We have implemented |specLangJS seqf| for Node.js in the form of a
library, without modifying Node.js or the V8 JavaScript engine.
%
Our implementation\footnote{Available at \codelink{}.} provides a
library for creating new tasks, i.e., contexts whose global object
only contains the standard JavaScript library and our IFC primitives
(e.g., |send| and |sandbox|).
%
When mapped to our formal treatement, |sandbox| is defined with |ap
klone tS = tS0|, where |tS0| is the global object corresponding to the
standard JavaScript library and our IFC primitives.
%
%These tasks can communicate and create new tasks, in turn.
%
These IFC operations are mediated by the trusted library code (executing
as the main Node.js context), which tracks the state (current label, messages,
etc.) of each task.  An example for |send|/|recv| is shown in
Figure~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
We remark that our system conservatively restricts
the kinds of messages that can be exchanged, via |send| (and |sandbox|),
to string values.
%
(We provide a convenience library which marshalls JSON objects to/from strings.)
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%

While the described system implements |specLangJS seqf|, applications
typically require access to libraries (e.g., the file system library
\textsf{fs}) that that have external effects.
%
Exposing the Node.js APIs directly to sandboxed tasks is unsafe.
Instead, we implement libraries such as a labeled \textsf{fs} as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Figure~\ref{fig:node}) and the main Node.js task that implements
the IFC monitor.
%
While this is safer than simply wrapping unsafe objects, adding
featuers such as the \textsf{fs} requires the code in the main task to
ensures that labels are properly propagated and enforced.
%
Unfortunately, while imposing such a proof burden
is undesirable, this also has to be expected:
different language environments expose different libraries for
handling external I/O, and the correct treatment of external effects
is application specific.
%
%% For instance, in the case of Node.js, how labels interact with the
%% file system may even vary according to the application (e.g.,
%% in the IFC system Hails~\cite{hails}, labels are not persisted).
%
%While we can extend our formalism to model a particular interface to
%the file system, HTTP client, etc. the utility of this formalization is
%unclear and left to future work.
%
We do not extend our formalism to account for the  particular
interface to the file system, HTTP client, etc., as this is
specific to the Node.js implementation and does not generalize
to other systems.

\subsubsection{Client-side COWL IFC:}\
We now describe some of the implementation aspects of
COWL, a JavaScript implementation of coarse-grained
IFC for Mozilla's Gecko.  This work provides the formal basis for
the implementation, and COWL is described in much more detail in~\cite{swapi}.
%
Since the architecture of COWL is similar to that of Node.js, we focus
on the main differences.
